---
title: "Dyanmic Treatment Rule"
author: "Lina Montoya and Nina Magnuson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  library(DTR), 
  library(SuperLearner),
  library(hitandrun)
)
```

## Description
DTR computes the simple or optimal dynamic treatment rule for data of the form $O = (W, A, Y) \sim P_0$. $W$ represents pretreatment covariates. $A$ is a binary variable indicating whether treatment was received. $Y$ is a variable for the outcome. Using DTR, we can compute the difference in expected outcome under a dynamic treatment rule (simple or optimal) versus expected outcome under a comparison group. This allows us to analyze the efficacy of different treatment regimes on the outcome. 


## Example Using Simulated Data

In order to illustrate the use of DTR, first use the data.simulation function to generate some data of the correct format. Next we must define the relevant variables from this data for reading into odtr and sdtr. The rule, which is an argument for sdtr, can be generated using one of the covariates, as shown below. This rule represents a simple treatment regime, for instance administering treatment based on individual preference. We advise assigning *QAW.SL.library* as shown below to ensure the correct form, but this is customizable, read sdtr help file on how to make your own.

```{r}
set.seed(37982)
data <- data.simulation(n=1000)
W = data[,grep("W", names(data))]
W_for_g = subset(W, select = c(W1, W2))
A = data$A
a = 0
Y = data$Y
rule = ifelse(data$W2 > 0, 1, 0) #for simple dynamic treatment 
#here based only on covariate W2
QAW.SL.library = "SL.correct"
head(data)
```
The data generated contains columns for covariates $W$, treatment $A$, and outcome $Y$ as described above. 

## Finding Simple Dynamic Treatment Rule

Sdtr will analyze the difference between the above mentioned, simple rule, and the comparison group.

```{r}
resultssimple = sdtr(W = W, W_for_g = W, a = a, A = A, Y = Y, 
                              rule = rule, 
                              QAW.SL.library = QAW.SL.library)
resultssimple
```

The outputted results from sdtr include *TMLE_simple*, the difference in mean outcome under a simple dyanmic treatment regime minus the mean outcome under a comparison group, estimated by targeted maximum likelihood estimator. Additionally, the 95% lower and upper bound for this estimator are outputted. This value indicates that the simple dynamic treatment rule results in higher expected outcome than the comparison group, an argument in favor of the simple rule. 

## Finding Optimal Dynamic Treatment Rule

Next we will find the optimal dynamic treatment rule for this simulated data using function odtr. The optimal dynamic treatment rule is the treatment regime that results in the optimal expected outcome. This provides the best method of assigning treatment specific to an individuals covariates. 

```{r, warning=FALSE, message=FALSE}
# note V must contain W_for_g, find to make V=W_for_g as it is here
V = subset(W, select = c(W1, W2))
grid.size = 100 #default 
risk.type = "empirical" #default 
QAV.SL.library = c("SL.glm", "SL.glmnet", "SL.mean")
resultsODTR = odtr(W = W, A = A, a = a, Y = Y, V = V, W_for_g = W_for_g,
                          QAW.SL.library = QAW.SL.library, 
                          QAV.SL.library = QAV.SL.library,
                          risk.type = risk.type,
                          grid.size = grid.size)
resultsODTR
```

Displayed above are the results from odtr function. The first, *TMLE_ODTR* is the difference in expected outcome under the optimal dynamic treatment rule minus the expected outvome in the comparison group, estimated by targeted maximum likelihood estimation, and where the risk type for obtaining the optimal rule is also targeted maximum likelihood estimation. The *CV.TMLE_ODTR* is this quantity computed using cross validation (CV TMLE estimation method), where $V=10$ folds are used by default. The upper and lower bounds for both quantities are outputted as well and labeled as 1 for lower bound and 2 for upper bound. 

The output for this simulated data set indicates that the optimal dynamic treatment rule outperformed the comparison group, ($a=0$, or no treatment). The confidence intervals indicate that this result is not trivial because the interval does not contain zero. Additionally, when compared with the output from sdtr, we see that the optimal dynamic treatment rule performed better than the simple dynamic treatment rule created based on one of the covariates, $W2$. As expected, the optimal dynamic treatment rule performed the best, creating a treatment regime that optimizes mean outcome. 
